Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-02-05 causal-bandit/icml-2015/discussion.tex
updated comment in discussion

\paragraph{Causal Models with Non-Observable Variables}
If we assume knowledge of the conditional \textit{interventional} distributions $P_a$ our analysis applies unchanged to the case of causal models with non-observable variables. For example, if we had access to a data set of \textit{experiments} in which the reward variable $Y$ was not available from which to build estimates of $P_a$. Some of the interventional distributions $P_a$ may be non-identifiable meaning we can not obtain prior estimates for $P_a$ from even an infinite amount of observational data. \todof{tie in to brief discussion of approach if had to estimate $P_a$ terms within algorithm.}

>>>>

\paragraph{Causal Models with Non-Observable Variables}
If we assume knowledge of the conditional \textit{interventional} distributions $P_a$ our analysis applies unchanged to the case of causal models with 
non-observable variables. For example, if we had access to a data set of \textit{experiments} in which the reward variable $Y$ was not 
available from which to build estimates of $P_a$. Some of the interventional distributions $P_a$ may be non-identifiable meaning we can not obtain prior estimates for $P_a$ from 
even an infinite amount of observational data. Even if all variables are observable and the graph is known, if the conditional distributions are unknown, then Algorithm
\ref{alg:general} cannot be used. Estimating these quantities will simultaneously minimising the simple regret is an interesting and challenging open problem.
